\documentclass{article} % Document class
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath,amsfonts,amssymb,amsthm} % Most useful ams packages
\usepackage{danielmacros,danielenv} % My packages
\usepackage{hyperref} % Hyperlinks
\usepackage{enumitem} % Nicer numbered lists
\usepackage{tikz-cd,quiver} % Commutative diagrams
\usepackage{todonotes} % TODO notes
\usepackage[scr=boondox]{mathalfa}
\usepackage[backend=bibtex, style=alphabetic]{biblatex}
\addbibresource{bibliography.bib}
%\usepackage{parskip}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=cyan,
} % Link colors

\title{\textsc{Introduction to Symplectic Geometry\\ Notes from Summer Semester 2025}}
\author{Daniel Arone}
\date{\today}

\begin{document}

\maketitle

These notes are on the course V5D6 - Introduction to Symplectic Geometry\footnote{\href{https://www.math.uni-bonn.de/~lcote/V5D6_2025.html}{https://www.math.uni-bonn.de/\textasciitilde lcote/V5D6\_2025.html}}, lectured jointly by Nathaniel Bottman and  Laurent Côté.
They are entirely my own, as are any potential mistakes in what follows.
Proceed with caution.
These notes are available on \href{https://github.com/Daniel-Arone/Symplectic-Geometry-Notes}{GitHub} and \href{https://www.overleaf.com/read/mhzgkjbnvkbg#3ec4a7}{Overleaf}.

This course covers the basic topics in symplectic geometry.
We will not discuss Floer theory or $J$-holomorphic curves.
The main reference for this course is \cite{intro} by McDuff and Salamon.

\tableofcontents

\pagebreak

\section{Introduction to symplectic topology}
\newlecture{(10.04.25).}
\input{lectures/lecture1.tex}

\newlecture{(17.04.25).}
\input{lectures/lecture2.tex}

\section{Dynamics and integrable systems}
\newlecture{(24.04.25).}
\input{lectures/lecture3.tex}

\newlecture{(08.05.25).}
\input{lectures/lecture4.tex}

\section{Lagrangian submanifolds and toric symplectic manifolds}
\newlecture{(15.05.25).}
\input{lectures/lecture5.tex}

\newlecture{}
\input{lectures/lecture6.tex}

\section{Symplectic capacities and embeddings}
\newlecture{}
\input{lectures/lecture7.tex}

\newlecture{}
\input{lectures/lecture8.tex}

\newlecture{}
\input{lectures/lecture9.tex}

\newlecture{}
\input{lectures/lecture10.tex}

\section{Hamiltonian dynamics}
\newlecture{}
\input{lectures/lecture11.tex}

\printbibliography

\end{document}
